The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study

### 2022-02-02 paper.tex
update

\section{Introduction}
The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
two giant bubbles symmetrically extending about 50 degrees above and below the Galactic center,
is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.

@@

Over the course of a decade,\
the first all-sky survey X-ray data with high-spatial resolution \citep{Predehl2021}\
from eROSITA \citep{Predehl2020} also reveals\
a large hourglass-shaped structure (eROSITA bubbles, hereafter) at the GC,\
symmetrically extending about 80 degress above and below GC.

The large-scale X-ray structure\
shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
and has remarkable morphological similarities to the Fermi bubbles.

The Fermi and eROSITA bubbles (collectiely we called the Galactic bubbles)

Early attempts to model the Fermi bubbles assumed that the jet is vertial to the Galactic plane...

>>>>

\section{Introduction}
The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
two large bubbles symmetrically extending about 50 degrees above and below the Galactic center,
is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.

@@

Over the course of a decade,\
the first all-sky survey X-ray data with high-spatial resolution \citep{Predehl2021}\
from eROSITA \citep{Predehl2020} also reveals\
a giant hourglass-shaped structure (eROSITA bubbles, hereafter) at the GC,\
symmetrically extending about 80 degress above and below GC.

The large-scale X-ray structure\
shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
and has remarkable morphological symmetry about the Galactic plane as the Fermi bubbles.

Their symmetry about the GC suggests that they originate\
from powerful energy injections from the GC, possibly related to nuclear star formation\
\citep{PhysRevLett.106.101102,Carretti2013}
or past active galactic nucleus (AGN) activity \citep{Guo2012,Yang2017}.

Early attempts to model the Fermi and eROSITA bubbles (collectiely we called the Galactic bubbles)\
assumed that the jet is vertial to the Galactic plane...
